Language-Based Security for Low-Level MPC

### 2024-09-02 ppdp24/slides.tex
checkpoint

  Existing HLLs rely on low-level MPC protocols with correctness
  assumed.
  \begin{itemize}
  \item Low-level protocols possess distinct features, e.g., probabilistic sampling.
  \item Existing proof techniques manual, error prone, complex security model.
  \end{itemize}
  Our contributions:
  \begin{itemize}
  \item Language design for low-level protocol definitions.
  \item (Re)formulation of security mode as \cemph{hyperoperties} (e.g., noninterference).
  \item Automated proof techniques.
  \end{itemize}

@@

>>>>

  Existing HLLs rely on low-level MPC protocols with correctness
  assumed.
  \begin{itemize}
  \item Low-level protocols possess distinct features, e.g., probabilistic sampling.
  \item Existing proof techniques manual, error prone, complex security model.
  \end{itemize}
  Our contributions:
  \begin{itemize}
  \item Language design for low-level protocol definitions.
  \item (Re)formulation of security mode as \cemph{hyperproperties} (e.g., noninterference).
  \item Automated proof techniques.
  \end{itemize}

@@

\begin{frame}{Circuits and Gates}

  Low-level protocols such as YGC and GMW implement $\idealf$ as a \cemph{circuit}.
  \begin{itemize}
  \item Composed by combing-- aka ``wiring''-- \cemph{gates}.
  \item Each gate standard definition, supports primitive $\fplus$ and $\ftimes$.
  \item Two input wires, one output wire, values remain encrypted on wire. 
  \end{itemize}
